Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-02 paper.tex
Add nsns figures; also force H float placement

% packages
\usepackage{amssymb}              % for \gtrsim ...
\usepackage{amsmath}              % for \text, align, split ...
\usepackage{color}                % for colorful margin notes
\usepackage[mathscr]{euscript}    % for \mathscr
\usepackage{graphicx}             % for \includegraphics
\usepackage{hyperref}             % for \url and \href
\usepackage{listings}             % for typesetting code with \lstinline
\usepackage{tabularx}             % for tabularx

@@

@@

\subsection{Hypermassive Neutron Star Remnant:
  Testing Everything}
\label{ssec:test_disk_comparison}
[Compute total and relative number and energy luminosities for a disk evolved
in one of \cite{fouc2015-m1_nsbh, fouc2016-m1_nsns, fouc2016-m1_evolve_n}.
Expect agreement within factors of a few (?).]
\todo{compute luminosities from M1 and RT, present table}

@@

The merger models are described in \cite{fouc2015-m1_nsbh, fouc2016-m1_nsns}.
Something like this is presented in \cite[Figs.~10-11]{pere2014-nu_wind};
compare.]
\todo{compute $H^r(\mu;\varepsilon)$ in nsns and nsbh}
\todo{compute $\langle \varepsilon \rangle(\mu)$}

\subsection{Neutrino Self-Interaction Potential}
\label{ssec:V_nunu}
In this section we present $V_{\nu\nu,0}$ along one test trajectory in the NSNS
model, and show that including elastic scattering makes a qualitative
difference in the character of the flavor evolution.

>>>>

% packages
\usepackage{amssymb}              % for \gtrsim ...
\usepackage{amsmath}              % for \text, align, split ...
\usepackage{color}                % for colorful margin notes
\usepackage[mathscr]{euscript}    % for \mathscr
\usepackage{float}                % for better control of figure placement
\usepackage{graphicx}             % for \includegraphics
\usepackage{hyperref}             % for \url and \href
\usepackage{listings}             % for typesetting code with \lstinline
\usepackage{tabularx}             % for tabularx

@@

% force all figures to be placed right where they are in the text
\floatplacement{figure}{H}

@@

\subsection{Hypermassive Neutron Star Remnant:
  Testing Everything}
\label{ssec:test_disk_comparison}
Total and relative number and energy luminosities for the disk evolved
in \cite{fouc2016-m1_evolve_n}.
Agreement better than 10\%.
\todo{put in table comparison M1 and RT}

\begin{figure}
  \includegraphics[width=\columnwidth]{production-colormap-merid-rho}
  \caption{A meridional slice of density in the hypermassive neutron
    star and disk configuration.}
  \label{fig:nsns_rho_merid}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{production-colormap-equat-rho}
  \caption{An equatorial slice of density in the hypermassive neutron
    star and disk configuration.}
  \label{fig:nsns_rho_equat}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{production-colormap-merid-temp}
  \caption{A meridional slice of temperature in the hypermassive neutron
    star and disk configuration.}
  \label{fig:nsns_temp_merid}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{production-colormap-equat-temp}
  \caption{A meridional slice of temperature in the hypermassive neutron
    star and disk configuration.}
  \label{fig:nsns_temp_equat}
\end{figure}

@@

The merger models are described in \cite{fouc2015-m1_nsbh, fouc2016-m1_nsns}.
Something like this is presented in \cite[Figs.~10-11]{pere2014-nu_wind};
compare.

\subsection{Neutrino Self-Interaction Potential}
\label{ssec:V_nunu}
In this section we present $V_{\nu\nu,0}$ along one test trajectory in the NSNS
model, and show that including elastic scattering makes a qualitative
difference in the character of the flavor evolution.
See Figs.~\ref{fig:V_nunu-noscat} and \ref{fig:V_nunu-scat}.

\begin{figure}
  \includegraphics[width=\columnwidth]{20170619-potentials-Vnue_Vnua_Vnu-000Mo-022deg-noscat}
  \caption{Neutrino self-interaction potential along a test trajectory
    originating at the surface of the hypermassive neutron star, and
    proceeding outward along a radial coordinate ray with angle
    $\psi=22^{\circ}$ with respect to the polar axis.
    The trajectory is parameterized by the coordinate length $s$.
    This calculation was done with scattering turned off.
    Outside of the symmetric point at $s\sim4km$, the potential is
    positive, i.e.\ $\nu_e$-dominated.
    Compare to Fig.~\ref{fig:V_nunu-scat}.
    }
  \label{fig:V_nunu-noscat}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{20170619-potentials-Vnue_Vnua_Vnu-000Mo-022deg-scat}
  \caption{Same as Fig.~\ref{fig:V_nunu-noscat},
    but with scattering turned on.
    Unlike the case with scattering turned off, here the potential is
    everywhere negative, i.e.\ $\bar{\nu}_e$-dominated.
    }
  \label{fig:V_nunu-scat}
\end{figure}
